### 2016-05-19 text/MS.Rmd
more adjustments to language and text

Centre for Geometric Biology / School of Biological Sciences, Monash University, Clayton, Victoria, Australia 3800  
\*Corresponding author: barnechedr@gmail.com

**Summary**

@@

Metabolic theories seek to unite hierarchical levels of biological organisation based on the scaling of energetic demands (i.e. metabolic rates), from individuals to ecosystems `r myCite(c('nisbet2000janimecol', 'brown2004', 'vandermeer2006tree'))`. The role of individual body mass, $M_i$, as a determinant of individual-level metabolic rate, $B_i$, is key to this goal. Myriad studies have examined the relationship between $B_i$ and $M_i$ `r myCite(c('kleiber1932', 'kleiber1961', 'peters1983', 'schmidtnielsen1984', 'glazier2005biolrev', 'delong2010', 'glazier2010biolrev'))`, typically revealing a power function of the form $B_i = B_oM_i^{\alpha}$, where $B_o$ is a normalisation constant independent of mass and $\alpha$ is a dimensionless scaling exponent. For most animals, $B_i$ scales sub-linearly (or negatively allometric, sensu `r myCite('huxley1932')`) with $M_i$, i.e. with $\alpha$ < 1, generally falling between 0.5 and 1. Importantly, $\alpha$ estimates can also vary considerably among taxa and with many biotic and abiotic variables (e.g. `r myCite(c('lovegrove2000amnat', 'moses2008amnat', 'white2009evolution', 'delong2010', 'killen2010ele', 'kolokotrones2010nature', 'vaca2010biollett', 'glazier2011ecolmongr', 'ketola2012jlinsoc', 'white2012procb', 'white2013jcompphysb', 'barneche2014ele', 'hirst2014ele'))`). While these studies demonstrate clearly that the value of $\alpha$ is not fixed, most share a common limitation: they rely on pre-existing differences in mass. Such correlative studies cannot address the causal association between $B_i$ and $M_i$ properly, because $M_i$ is correlated with a range of other environmental, physiological, and life history variables (see e.g. `r myCite(c('peters1983', 'calder1984book', 'schmidtnielsen1984'))` for comprehensive reviews) and many of these variables are also associated with $B_i$ `r myCite(c('mcnab2002book', 'konarzewski2013jcompphysb', 'white2013jcompphysb'))`.

@@

Experimental size manipulation in colonial organisms also allows for tests of how ecological processes such as predation or disturbance affect individual physiology. For instance, it has been demonstrated that mimicking the effects of partial predation or physical disturbance through experimental size manipulation yields different responses in growth and reproductive onset in one arborescent (no effects on growth, delayed reproduction and reduced fecundity; `r myCite('bone2005jembe')`) and one encrusting bryozoan (reduced growth, with reproductive onset and fecundity dependent on the age of remaining zooids; `r myCite('hart2009ecologyb')`). On the other hand, size manipulations on one encrusting bryozoan `r myCite('white2011amnat')` and one colonial ascidian `r myCite('nakaya2005procb')` only affected the size of individuals, such that the scaling relationships between metabolic rate and colony size did not differ between size-manipulated and unmanipulated colonies. Sub-linear allometric scaling, in turn, implies that mass-specific metabolic rates decrease with size, and therefore changes in size structure will influence total population- and community- level respiration flux (if total standing biomass is held fixed; `r myCite(c('allen2005', 'barneche2014ele'))`). Meanwhile, resource ingestion rates appear to scale linearly with size, in some colonial organisms at least (e.g. `r myCite('pratt2005meps')`), suggesting that these two key processes -- energy ingestion and expenditure -- scale very differently with colony size. These different scaling relationships suggest that larger colonies have an energetic advantage over smaller colonies, although this remains to be tested.

@@

**Material and Methods**

*1. Animal collections*  
To collect our study organisms, roughened acetate sheets secured to the underside of 6 mm thick PVC sheets suspended from floating pontoons at a depth of 1 m were deployed at Manly Boat Harbour, Queensland, Australia (27˚27' S, 153˚11' E) and checked regularly to remove fouling organisms other than our species of interest: *Bugula neritina* and *B. stolonifera* (arborescent bryozoans that have a three dimensional tree-like growth form), *Hippopodina iririkiensis* (an encrusting bryozoan that grows mostly in two dimensions as flat disc), and an unidentified species of sponge belonging to the Microcionidae family (`r myCite('hart2009ecology')`; again a flat species that grows mostly in two dimensions) (Table 1). After 6 weeks in the field (average SST 22 ˚C), sheets bearing colonies were returned to the University of Queensland where they were kept in aerated seawater tanks (18 ˚C) for up to 48 h prior to measurements. For encrusting colonies, sections of acetate bearing whole colonies were then cut from the sheets and fragmented (see e.g. `r myCite(c('nakaya2005procb', 'white2011amnat'))` for details and tests of potential experimental artefacts). Arborescent colonies were cut directly from the acetate sheets and fragmented.

@@

where $m_b$ is the rate of change of $\textrm{O}_\textrm{2}$ saturation for blank vials containing no bryozoans (\% h^-1^), ${\beta}_{\textrm{O}_\textrm{2}}$ is the oxygen capacitance of air-saturated sea water at 10 ˚C (6.4 ml l^-1^) or 25 ˚C (4.74 ml l^-1^) `r myCite('cameron1986book')` and $V$ is water volume (vials were 0.005 l in volume and water volume was calculated by subtracting the volume of acetate and animals). At least four blank vials were recorded simultaneously with each 24-well plate to account for microbial oxygen consumption and sensor spots were calibrated with air-saturated seawater (100\% A.S.) and water containing 2\% sodium sulfite (0\% A.S.). After a 1 h setting period (i.e. time necessary for the system to come into equilibrium), $\dot{V}\textrm{O}_\textrm{2}$ measurements lasted up to 20 h depending on individual mass (minute individuals require longer periods of time in order to detect $\dot{V}\textrm{O}_\textrm{2}$ signals). Following measurement of $\dot{V}\textrm{O}_\textrm{2}$, colonies or fragments were blotted dry and weighed to 0.1 mg (Sartorius A 200 S, Sartorius AG, Göttingen, Germany). All measurements of $\dot{V}\textrm{O}_\textrm{2}$ were made in one of four dark constant temperature cabinets, with temperatures within a run randomised among cabinets.

@@

where mass (mg), $\textrm{ln}M_i$, is a continuous variable, while temperature (two levels: 10 ˚C and 25 ˚C) and species (four levels corresponding to the four species) are categorical variables. With this model, we allow each species to have a different mass-scaling slope that may change with temperature; we also account for species- and temperature-specific deviations on the metabolic normalisation (i.e. statistical model). We also included date of experiment, $\Delta D$ as a random effect on the metabolic normalisation to help control for natural experimental variability. We then performed a model selection procedure (see below) by comparing the above full model with a series of nested two- and one-way interaction models in order to formally test for mass-temperature interactions in metabolic rates among different species.

@@

The model selection indicated that the three-way interaction model (equation 2) performed significantly better than all nested two- and one-way interaction models (Table 2), thus implying that different species present different interactions between mass-scaling and temperature dependence. Particularly, the best model yields no interaction between mass scaling and temperature dependence for *Bugula stolonifera* and the Microcionidae sponge (large overlap between 95\% credible intervals for the mass-scaling slopes, $\alpha$) (Fig. 1). Still, while the mass-scaling slopes are statistically the same between temperatures for these species, there is evidence for higher metabolic normalisations (i.e. intercepts), $B_o$, at higher temperatures (though marginally significant for Microcionidae, i.e. slight overlap between 95\% credible intervals). For example, metabolic rates increase `r rounded(exp(averageEstimates$lnB25[averageEstimates$species == 'Stolonifera'])/exp(averageEstimates$lnB10[averageEstimates$species == 'Stolonifera']))`-fold between 10 ˚C and 25 ˚C for *B. stolonifera*, yielding a $Q_{10}$ of `r rounded(q10andErs$q10[q10andErs$species == 'Stolonifera'])`, which is equivalent to an activation energy of `r rounded(q10andErs$er[q10andErs$species == 'Stolonifera'], 2)` eV `r myCite(c('gillooly2001','yvondurocher2012a'))`. The best model indicates that the difference in metabolic rates between 25 ˚C and 10 ˚C for *Hippopodina iririkiensis* decreases, on average, `r rounded(tempDeltas[1,'tempDelta'])`-fold moving from `r round(exp(2))` to `r round(exp(5))` mg. For *Bugula neritina*, however, rates increase `r rounded(1/tempDeltas[3,'tempDelta'])`-fold along the same body-mass gradient.

Average posterior estimates of mass-scaling exponents are inconsistent among the studied species and between growth forms (2D and 3D). For example, for organisms that exhibit 2D growth, *Hippopodina iririkiensis* shows exponents that encompass both 0.67 (Fractal geometry model prediction for 2D organisms; `r myCite('koontz2009amjbot')`) and 0.75 (Fractal geometry model prediction for 3D organisms; `r myCite(c('west1997science', 'west1999science'))`) at 10 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's10_97.5'], 2)`), but that are significantly shallower than 0.75 at 25 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's25_97.5'], 2)`). Microcionidae presents exponents that only overlap 0.67 at 10 ˚C, but not at 25 ˚C (95\% CI at 10 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's10_97.5'], 2)`; 95\% CI at 25 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's25_97.5'], 2)`). On the other hand, for 3D organisms, *Bugula neritina* presents scaling exponents that overlap both 0.67 and 0.75 at 25 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's25_97.5'], 2)`), but are significantly shallower at 10 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's10_97.5'], 2)`). Finally, *Bugula stolonifera* presents values that overlap both 0.67 and 0.75 at both temperatures (95\% CI at 10 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's10_97.5'], 2)`; 95\% CI at 25 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's25_97.5'], 2)`).

@@

Here, we show experimentally that the mass-scaling of metabolic rates may change with temperature, and in different ways across different species of marine invertebrates and between growth forms. We thus add to recent empirical evidence documenting mass-temperature interactions in metabolic rates (e.g. `r myCite(c('killen2010ele', 'glazier2005biolrev'))`). Possibly, the ability of our studied species to acclimate upon acute temperature changes could have affected the results (see discussion in `r myCite('glazier2014systems')`). Our experimental set up, however, randomised species and individual sizes across temperatures such that systematic effects across sizes or among species are unlikely. Moreover, the temperature ranges span those experienced by these species in the field. Still, if mass-temperature interactions are proven to be frequent and consistent across different types of organisms, future studies will be necessary to mechanistically explain the interactive effects between mass scaling and temperature dependence of biological rates (but see the metabolic-level boundaries hypothesis in `r myCite(c('glazier2005biolrev', 'glazier2010biolrev', 'glazier2014systems'))`).

@@

While the mass scaling exponent was unaffected by temperature for two species (*Bugula stolonifera* and Microcionidae), it decreased and increased for one encrusting (*Hippopodina iririkiensis*) and one arborescent species (*Bugula neritina*), respectively. These results imply that energy use may vary for the same species in different environments, possibly affecting their ultimate colonisation success and abundance. For example, the fact that *Bugula neritina* presented a shallower mass-scaling exponent at colder temperatures possibly indicates that large cold-environment individuals are more efficient in spending energy than counterparts in warm environments. On the other hand, our results indicate that *Hippopodina iririkiensis* presents a reduction in metabolic benefits of attaining a larger size at colder temperatures. Importantly, though, we note that there are many extrinsic factors that may affect abundance and selection on body size (e.g. predation, competition). Nonetheless, such differentials in the costs and benefits of attaining large size may help explain why some species living in cold temperatures present a slower pace of life (e.g. `r myCite('rosa2010jmba')`). Moreover, incorporation of differences in the size-dependence of the costs and benefits of size might improve current attempts to scale up energy from individuals to higher levels of organisation (e.g. `r myCite(c('allen2005','yvondurocher2012b','barneche2014ele','barneche2016procb'))`).

@@

**Table 2.** The best model was constructed, using the R package *lme4*, by successively removing fixed effects based on likelihood ratio tests of significance `r myCite('zuur2009book')`. In the table, $\chi^2$ and d.f. refer to likelihood ratio test between the full model and nested model. The final best model, which includes all parameters, is indicated in bold.

**Figures**

*Figure 1.* Estimates from the three-way interaction model as obtained by Bayesian methods in *JAGS*. Results for each species are represented in groups of four plots, with blue and red colours representing actual data and parameter estimates at 10 ˚C and 25 ˚C, respectively. *Top-left* and *bottom-right*: posterior probabilities of mass-scaling exponents and metabolic normalisations (respectively), with bars over curves representing 95\% credible intervals, and numbers representing average estimates. *Bottom-left*: covariance between mass-scaling exponents and metabolic normalisations for each of the 10,000 MCMC iterations (translucent circles), with overlaid density heat-map. *Top-right*: regressions of individual metabolic rate, $\textrm{ln}B_i$, as functions of individual body mass, $\textrm{ln}M_i$. Regression fits were plotted using the average from the posterior distributions. In probability posterior plots (*top-left* and *bottom-right*), smooth probability curves (*n* = 511 values) were approximated from posterior probability density curves (*n* = 512 values); differences between adjacent $x$ values (i.e. parameter estimates) were multiplied by the average of adjacent $y$ values (i.e. respective probability density values; $(x_{i+1} - x_{i}) \times ((y_{i+1} - y_{i})/2)$) thus insuring that the integral of the probability curve $\approx$ 1.

>>>>

\*Corresponding author: barnechedr@gmail.com

Affiliation:  
Centre for Geometric Biology / School of Biological Sciences, Monash University, Clayton, Victoria, Australia 3800

**Abstract**

@@

Metabolic theories seek to unite hierarchical levels of biological organization based on the scaling of energetic demands (i.e. metabolic rates), from individuals to ecosystems `r myCite(c('nisbet2000janimecol', 'brown2004', 'vandermeer2006tree'))`. The role of individual body mass, $M_i$, as a determinant of individual-level metabolic rate, $B_i$, is key to this goal. Myriad studies have examined the relationship between $B_i$ and $M_i$ `r myCite(c('kleiber1932', 'kleiber1961', 'peters1983', 'schmidtnielsen1984', 'glazier2005biolrev', 'delong2010', 'glazier2010biolrev'))`, typically revealing a power function of the form $B_i = B_oM_i^{\alpha}$, where $B_o$ is a normalization constant independent of mass and $\alpha$ is a dimensionless scaling exponent. For most animals, $B_i$ scales sub-linearly (or negatively allometric, sensu `r myCite('huxley1932')`) with $M_i$, i.e. with $\alpha$ < 1, generally falling between 0.5 and 1. Importantly, $\alpha$ estimates can also vary considerably among taxa and with many biotic and abiotic variables (e.g. `r myCite(c('lovegrove2000amnat', 'moses2008amnat', 'white2009evolution', 'delong2010', 'killen2010ele', 'kolokotrones2010nature', 'vaca2010biollett', 'glazier2011ecolmongr', 'ketola2012jlinsoc', 'white2012procb', 'white2013jcompphysb', 'barneche2014ele', 'hirst2014ele'))`). While these studies demonstrate clearly that the value of $\alpha$ is not fixed, most share a common limitation: they rely on pre-existing differences in mass. Such correlative studies cannot address the causal association between $B_i$ and $M_i$ properly, because $M_i$ is correlated with a range of other environmental, physiological, and life history variables (see e.g. `r myCite(c('peters1983', 'calder1984book', 'schmidtnielsen1984'))` for comprehensive reviews) and many of these variables are also associated with $B_i$ `r myCite(c('mcnab2002book', 'konarzewski2013jcompphysb', 'white2013jcompphysb'))`.

@@

Experimental size manipulation in colonial organisms also allows for tests of how ecological processes such as predation or disturbance affect individual physiology. For instance, it has been demonstrated that mimicking the effects of partial predation or physical disturbance through experimental size manipulation yields different responses in growth and reproductive onset in one arborescent (no effects on growth, delayed reproduction and reduced fecundity; `r myCite('bone2005jembe')`) and one encrusting bryozoan (reduced growth, with reproductive onset and fecundity dependent on the age of remaining zooids; `r myCite('hart2009ecologyb')`). On the other hand, size manipulations on one encrusting bryozoan `r myCite('white2011amnat')` and one colonial ascidian `r myCite('nakaya2005procb')` only affected the size of individuals, such that the scaling relationships between metabolic rate and colony size did not differ between size-manipulated and non-manipulated colonies. Sub-linear allometric scaling, in turn, implies that mass-specific metabolic rates decrease with size, and therefore changes in size structure will influence total population- and community- level respiration flux (if total standing biomass is held fixed; `r myCite(c('allen2005', 'barneche2014ele'))`). Meanwhile, resource ingestion rates appear to scale linearly with size, in some colonial organisms at least (e.g. `r myCite('pratt2005meps')`), suggesting that these two key processes -- energy ingestion and expenditure -- scale very differently with colony size. These different scaling relationships suggest that larger colonies have an energetic advantage over smaller colonies, although this remains to be tested.

@@

**Methods**

*1. Animal collections*  
To collect our study organisms, roughened acetate sheets secured to the underside of 6 mm thick PVC sheets suspended from floating pontoons at a depth of 1 m were deployed at Manly Boat Harbour, Queensland, Australia (27˚27' S, 153˚11' E) and checked regularly to remove fouling organisms other than our species of interest: *Bugula neritina* and *B. stolonifera* (arborescent bryozoans that have a three dimensional tree-like growth form), *Hippopodina iririkiensis* (an encrusting bryozoan that grows mostly in two dimensions as flat disc), and an unidentified species of sponge belonging to the Microcionidae family (`r myCite('hart2009ecology')`; again a flat species that grows mostly in two dimensions) (Table 1). After 6 weeks in the field (average SST 22 ˚C), sheets bearing colonies were returned to the University of Queensland where they were kept in aerated seawater tanks (18 ˚C) for up to 48 h prior to measurements. For encrusting colonies, sections of acetate bearing whole colonies were then cut from the sheets and fragmented (see e.g. `r myCite(c('nakaya2005procb', 'white2011amnat'))` for details and tests of potential experimental artifacts). Arborescent colonies were cut directly from the acetate sheets and fragmented.

@@

where $m_b$ is the rate of change of $\textrm{O}_\textrm{2}$ saturation for blank vials containing no bryozoans (\% h^-1^), ${\beta}_{\textrm{O}_\textrm{2}}$ is the oxygen capacitance of air-saturated sea water at 10 ˚C (6.4 ml l^-1^) or 25 ˚C (4.74 ml l^-1^) `r myCite('cameron1986book')` and $V$ is water volume (vials were 5 ml in volume and water volume was calculated by subtracting the volume of acetate and animals). At least four blank vials were recorded simultaneously with each 24-well plate to account for microbial oxygen consumption and sensor spots were calibrated with air-saturated seawater (100\% A.S.) and water containing 2\% sodium sulfite (0\% A.S.). After a 1 h setting period (i.e. time necessary for the system to come into equilibrium), $\dot{V}\textrm{O}_\textrm{2}$ measurements lasted up to 20 h depending on individual mass (tiny individuals require much longer measurement periods in order to detect $\dot{V}\textrm{O}_\textrm{2}$). Following measurement of $\dot{V}\textrm{O}_\textrm{2}$, colonies or fragments were blotted dry and weighed to 0.1 mg (Sartorius A 200 S, Sartorius AG, Göttingen, Germany). All measurements of $\dot{V}\textrm{O}_\textrm{2}$ were made in one of four dark constant temperature cabinets, with temperatures within a run randomized among cabinets.

@@

where mass, $\textrm{ln}M_i$ (mg), is a continuous variable, while temperature (two levels: 10 ˚C and 25 ˚C) and species (four levels corresponding to the four species) are categorical variables. With this model, we allow each species to have a different mass-scaling slope that may change with temperature; we also account for species- and temperature-specific deviations on the metabolic normalization (i.e. statistical model). We also included date of experiment, $\Delta D$ as a random effect on the metabolic normalization to help control for natural experimental variability. We then performed a model selection procedure (see below) by comparing the above full model with a series of nested two- and one-way interaction models in order to formally test for mass-temperature interactions in metabolic rates among different species.

@@

The model selection indicated that the three-way interaction model (equation 2) performed significantly better than all nested two- and one-way interaction models (Table 2), thus implying that different species present different interactions between mass-scaling and temperature dependence. Particularly, the best model yields no interaction between mass scaling and temperature dependence for *Bugula stolonifera* and the Microcionidae sponge (large overlap between 95\% credible intervals for the mass-scaling slopes, $\alpha$) (Fig. 1). Still, while the mass-scaling slopes are statistically the same between temperatures for these species, there is evidence for higher metabolic normalizations (i.e. intercepts), $B_o$, at higher temperatures (though marginally significant for Microcionidae, i.e. slight overlap between 95\% credible intervals; bottom-right quadrants in Fig. 1). For example, metabolic rates increase `r rounded(exp(averageEstimates$lnB25[averageEstimates$species == 'Stolonifera'])/exp(averageEstimates$lnB10[averageEstimates$species == 'Stolonifera']))`-fold between 10 ˚C and 25 ˚C for *B. stolonifera*, yielding a $Q_{10}$ of `r rounded(q10andErs$q10[q10andErs$species == 'Stolonifera'])`, which is equivalent to an activation energy of `r rounded(q10andErs$er[q10andErs$species == 'Stolonifera'], 2)` eV `r myCite(c('gillooly2001','yvondurocher2012a'))`. The best model indicates that the difference in metabolic rates between 25 ˚C and 10 ˚C for *Hippopodina iririkiensis* decreases, on average, `r rounded(tempDeltas[1,'tempDelta'])`-fold moving from `r round(exp(2))` to `r round(exp(5))` mg. For *Bugula neritina*, however, rates increase `r rounded(1/tempDeltas[3,'tempDelta'])`-fold along the same body-mass gradient.

Average posterior estimates of mass-scaling exponents (top-left quadrants in Fig. 1) are inconsistent among the studied species and between growth forms (2D and 3D). For example, for organisms that exhibit 2D growth, *Hippopodina iririkiensis* shows exponents that encompass both 0.67 (Fractal geometry model prediction for 2D organisms; `r myCite('koontz2009amjbot')`) and 0.75 (Fractal geometry model prediction for 3D organisms; `r myCite(c('west1997science', 'west1999science'))`) at 10 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's10_97.5'], 2)`), but that are significantly shallower than 0.75 at 25 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bryo', 's25_97.5'], 2)`). Microcionidae presents exponents that only overlap 0.67 at 10 ˚C, but not at 25 ˚C (95\% CI at 10 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's10_97.5'], 2)`; 95\% CI at 25 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Sponge', 's25_97.5'], 2)`). On the other hand, for 3D organisms, *Bugula neritina* presents scaling exponents that overlap both 0.67 and 0.75 at 25 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's25_97.5'], 2)`), but are significantly shallower at 10 ˚C (95\% CI: `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Bugula', 's10_97.5'], 2)`). Finally, *Bugula stolonifera* presents values that overlap both 0.67 and 0.75 at both temperatures (95\% CI at 10 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's10_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's10_97.5'], 2)`; 95\% CI at 25 ˚C: `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's25_2.5'], 2)` -- `r rounded(ci95Estimates[ci95Estimates$species == 'Stolonifera', 's25_97.5'], 2)`).

@@

Here, we show experimentally that the mass-scaling of metabolic rates may change with temperature, and in different ways across different species of marine invertebrates and between growth forms. We thus add to recent empirical evidence documenting mass-temperature interactions in metabolic rates (e.g. `r myCite(c('killen2010ele', 'glazier2005biolrev'))`). Possibly, the ability of our studied species to acclimate upon acute temperature changes could have affected the results (see discussion in `r myCite('glazier2014systems')`). Our experimental set up, however, randomized species and individual sizes across temperatures such that systematic effects across sizes or among species are unlikely. Moreover, the temperature ranges span those experienced by these species in the field. Still, if mass-temperature interactions are proven to be frequent and consistent across different types of organisms, future studies will be necessary to mechanistically explain the interactive effects between mass scaling and temperature dependence of biological rates (but see the metabolic-level boundaries hypothesis in `r myCite(c('glazier2005biolrev', 'glazier2010biolrev', 'glazier2014systems'))`).

@@

While the mass scaling exponent was unaffected by temperature for two species (*Bugula stolonifera* and Microcionidae), it decreased and increased for one encrusting (*Hippopodina iririkiensis*) and one arborescent species (*Bugula neritina*), respectively. These results imply that energy use may vary for the same species in different environments, possibly affecting their ultimate colonization success and abundance. For example, the fact that *Bugula neritina* presented a shallower mass-scaling exponent at colder temperatures possibly indicates that large cold-environment individuals are more efficient in spending energy than counterparts in warm environments. On the other hand, our results indicate that *Hippopodina iririkiensis* presents a reduction in metabolic benefits of attaining a larger size at colder temperatures. Importantly, though, we note that there are many extrinsic factors that may affect abundance and selection on body size (e.g. predation, competition). Nonetheless, such differentials in the costs and benefits of attaining large size may help explain why some species living in cold temperatures present a slower pace of life (e.g. `r myCite('rosa2010jmba')`). Moreover, incorporation of differences in the size-dependence of the costs and benefits of size might improve current attempts to scale up energy from individuals to higher levels of organization (e.g. `r myCite(c('allen2005','yvondurocher2012b','barneche2014ele','barneche2016procb'))`).

@@

*Table 2.* The best model was constructed, using the R package *lme4*, by successively removing fixed effects based on likelihood ratio tests of significance `r myCite('zuur2009book')`. In the table, $\chi^2$ and d.f. refer to likelihood ratio test between the full model and nested model. The final best model, which includes all parameters, is indicated in bold.

**Figure caption**

*Figure 1.* Estimates from the three-way interaction model as obtained by Bayesian methods in *JAGS*. Results for each species are represented in groups of four plots, with blue and red colors representing actual data and parameter estimates at 10 ˚C and 25 ˚C, respectively. *Top-left* and *bottom-right*: posterior probabilities of mass-scaling exponents and metabolic normalizations (respectively), with bars over curves representing 95\% credible intervals, and numbers representing average estimates. *Bottom-left*: covariance between mass-scaling exponents and metabolic normalizations for each of the 10,000 MCMC iterations (translucent circles), with overlaid density heat-map. *Top-right*: regressions of individual metabolic rate, $\textrm{ln}B_i$, as functions of individual body mass, $\textrm{ln}M_i$. Regression fits were plotted using the average from the posterior distributions. In probability posterior plots (*top-left* and *bottom-right*), smooth probability curves (*n* = 511 values) were approximated from posterior probability density curves (*n* = 512 values); differences between adjacent $x$ values (i.e. parameter estimates) were multiplied by the average of adjacent $y$ values (i.e. respective probability density values; $(x_{i+1} - x_{i}) \times ((y_{i+1} - y_{i})/2)$) thus insuring that the integral of the probability curve $\approx$ 1.
